%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.10in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Justin Siek} \\ \vspace{1pt}
    \href{https://justinsiek.com}{\underline{justinsiek.com}} $|$
    \href{mailto:siekj@uci.edu}{\underline{justinsiek05@gmail.com}} $|$ 
    \href{https://linkedin.com/in/justin-siek}{\underline{in/justin-siek}} $|$
    \small 208-971-4200
    
    
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Irvine}{\textbf{Graduation: Jun 2027}}
      {B.S Computer Science, Artificial Intelligence Specialization, Statistics Minor}{GPA: 3.76}
      \resumeItemListStart
        \resumeItem{Courses: ML and Data Mining, Data Structures and Algorithms, Computer Vision, Information Retrieval, Python}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Data Science Intern}{May 2025 -- Present}
      {First American Financial}{Santa Ana, CA}
      \resumeItemListStart
        \resumeItem{Built a knowledge graph with 500M+ nodes and 1.5B+ edges used by 3 production products; optimized storage systems and cloud infrastructure, using cloud SQL, indexing and code in Python/C++ for fast scalable queries.}
        \resumeItem{Developed a Graph Neural Network that predicted listing propensity with a 10\% lift over baseline; built a GraphRAG system on LangChain for NL queries, plus training pipelines, metrics and cloud inference prod.}
        \resumeItem{Triaged issues, root-caused failures and created monitoring metrics to scale services using Python and cloud.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{Sep 2024 -- Present}
      {ICS Student Council}{Irvine, CA}
      \resumeItemListStart
        \resumeItem{Built ZotMeet, a full-stack scheduling and study-room booking platform; designed scalable PostgreSQL schema with Drizzle ORM for optimized query performance and implemented responsive NextJS UI, SSR and REST endpoints.}
        \resumeItem{Collaborated with peers to plan, build and test fullstack ZotMeet features; instrumented dashboards monitoring PostgreSQL via Drizzle ORM, triaged incidents, root-caused failures and improved booking reliability.}
        \resumeItem{Built RESTful API endpoints and SSR pages in NextJS to power ZotMeet booking workflows with responsive UI.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
     \resumeProjectHeading
          {\textbf{Flywheel} $|$ \href{https://github.com/BOSSrobot/DubHacks2025}{\emph{Code}}}{PyTorch $|$ Hugging Face $|$ Statsig}
          \resumeItemListStart
            \resumeItem{Built an automated RLHF pipeline with PyTorch and Hugging Face to fine-tune dev tools using Direct Preference Optimization and QLora, enabling efficient 4-bit quantized model training from real A/B preference data.}
            \resumeItem{Designed and deployed an MCP server that auto-embeds Statsig A/B tests into apps to collect user preferences, feeding a vLLM inference stack and closed-loop retraining to scale model quality and support debug metrics.}
            \resumeItem{Deployed fine-tuned model on vLLM, closing the loop with Statsig A/B preferences to boost net model metrics.}
          \resumeItemListEnd
     \resumeProjectHeading
          {\textbf{MakerSafe (Cruzhacks Best Hardware Hack, Best Use of Viam)} $|$ \href{https://github.com/justinsiek/maker-safe}{\emph{Code}}}{OpenCV $|$ YOLOv8 $|$ NextJS}
          \resumeItemListStart
            \resumeItem{Engineered a Raspberry Pi edge system with three webcams, using Viam control plane to run OpenCV face detection and YOLOv8 PPE models per station, streaming events via WebSockets to a NextJS/Flask dashboard for safety.}
            \resumeItem{Won \emph{Best Use of Viam} and \emph{Best Hardware Hack} at CruzHacks (500 participants) for MakerSafe; led triage, built NextJS/Flask dashboards, analyzed metrics, and scaled monitoring across maker stations.}
            \resumeItem{Built PPE & identity enforcement using OpenCV and YOLOv8, streaming POSTs and WS events to NextJS dashboard.}
          \resumeItemListEnd
     \resumeProjectHeading
          {\textbf{hhana} $|$ \href{https://github.com/justinsiek/hhana}{\emph{Code}}}{Python $|$ Polars $|$ DuckDB}
          \resumeItemListStart
            \resumeItem{Designed ETL pipeline using Polars and DuckDB to process 10 million hand histories, feature-engineer population statistics, and feed aggregated datasets into models for exploit detection and monitoring in production.}
            \resumeItem{Implemented MCCFR baseline in Python to compute equilibrium strategies with softmax utility boosts, integrated exploit policies from population deviations, and produced metrics for debugging and cross-team triage.}
            \resumeItem{Used Python to speed ETL with Polars and DuckDB, optimize storage, and prepare models for production via CI}
          \resumeItemListEnd
     \resumeProjectHeading
          {\textbf{Apprazer (IrvineHacks Best Use Of AI In Real Estate)} $|$ \href{https://github.com/justinsiek/Apprazer}{\emph{Code}}}{OpenCV $|$ SKLearn $|$ NextJS}
          \resumeItemListStart
            \resumeItem{Led 4-person team to build loan pre-approval system, won \emph{Best Use of AI in Real Estate} at IrvineHacks with 600 participants; used OpenCV ROI to process 5\% of pages and achieve 99\% document parsing accuracy.}
            \resumeItem{Built Random Forest classifier with SKLearn on 5M+ records to decide loans, achieving 88\% accuracy; integrated into NextJS app with logging, metrics, CI, and cross-team testing for deployment. Enabled triage metrics.}
            \resumeItem{Reduced OCR cost by processing only 5\% of each page via OpenCV ROI, achieving 99\% document parsing accuracy.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, Java, JavaScript, TypeScript, SQL} \\
     \textbf{Frameworks}{: React, Next.js, Flask, Tailwind} \\
     \textbf{Libraries}{: numpy, pandas, OpenCV, Tensorflow, Pytorch, SKLearn} \\
     \textbf{Developer Tools}{: AWS, Docker, Git, Databricks, Snowflake, Postman, Playwright} 
     }}
 \end{itemize}


%-------------------------------------------
\end{document}
