%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.10in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Justin Siek} \\ \vspace{1pt}
    \href{https://justinsiek.com}{\underline{justinsiek.com}} $|$
    \href{mailto:siekj@uci.edu}{\underline{justinsiek05@gmail.com}} $|$ 
    \href{https://linkedin.com/in/justin-siek}{\underline{in/justin-siek}} $|$
    \small 208-971-4200
    
    
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Irvine}{\textbf{Graduation: Jun 2027}}
      {B.S Computer Science, Artificial Intelligence Specialization, Statistics Minor}{GPA: 3.76}
      \resumeItemListStart
        \resumeItem{Courses: ML and Data Mining, Data Structures and Algorithms, Computer Vision, Information Retrieval, Python}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Data Science Intern}{May 2025 -- Present}
      {First American Financial}{Santa Ana, CA}
      \resumeItemListStart
        \resumeItem{Built a massive knowledge graph with 500M+ nodes and 1.5B+ edges representing California property data, which powers 3 production products and supported GNN training to predict listing propensity with a 10\% lift.}
        \resumeItem{Designed and deployed a GraphRAG system on LangChain to enable conversational NL queries over the knowledge graph; implemented retrieval, vector store and PyTorch GNN inference, boosting analyst productivity and demos.}
        \resumeItem{Deployed PyTorch GNN for listing propensity, yielding a 10\% lift and shipping to production with CI & ops.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{Sep 2024 -- Present}
      {ICS Student Council}{Irvine, CA}
      \resumeItemListStart
        \resumeItem{Led development of ZotMeet, a fullstack platform for UCI students that enabled meeting scheduling and study room booking; designed scalable PostgreSQL schema and optimized queries using Drizzle ORM and migrations.}
        \resumeItem{Implemented NextJS fullstack features including responsive UI components, SSR and REST APIs; reduced perceived load time via caching and API pagination, improving scalability and concurrent user handling for scheduling.}
        \resumeItem{Authored REST APIs and NextJS SSR handlers for ZotMeet, enforcing DB constraints and improving query latency.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
     \resumeProjectHeading
          {\textbf{Flywheel} $|$ \href{https://github.com/BOSSrobot/DubHacks2025}{\emph{Code}}}{PyTorch $|$ Hugging Face $|$ Statsig}
          \resumeItemListStart
            \resumeItem{Built RLHF training pipeline in PyTorch and Hugging Face to optimize developer tools from real A/B experiments, implementing Direct Preference Optimization and QLora for efficient 4-bit quantized fine-tuning at scale.}
            \resumeItem{Developed an MCP server to let LLMs automatically embed A/B tests into applications and collect Statsig user-preference datasets; deployed fine-tuned models to a vLLM inference server to close the feedback loop securely.}
            \resumeItem{Closed loop: MCP server ingested Statsig A/B signals to refine models on vLLM for live improvement at scale.}
          \resumeItemListEnd
     \resumeProjectHeading
          {\textbf{MakerSafe (Cruzhacks Best Hardware Hack, Best Use of Viam)} $|$ \href{https://github.com/justinsiek/maker-safe}{\emph{Code}}}{OpenCV $|$ YOLOv8 $|$ NextJS}
          \resumeItemListStart
            \resumeItem{Won \emph{Best Use of Viam} and \emph{Best Hardware Hack} at CruzHacks (500 participants) for a real-time PPE and presence monitor using Raspberry Pi, Viam, OpenCV and YOLOv8 on three webcams (login + 2 station cameras).}
            \resumeItem{Engineered Raspberry Pi edge pipeline with Viam control plane to run OpenCV face detection and YOLOv8 PPE models per station; streamed events via POST and WebSockets to NextJS/Flask dashboard for live monitoring.}
            \resumeItem{Built end-to-end maker safety demo, streamed real-time station events to NextJS/Flask dashboard for judges.}
          \resumeItemListEnd
     \resumeProjectHeading
          {\textbf{Apprazer (IrvineHacks Best Use Of AI In Real Estate)} $|$ \href{https://github.com/justinsiek/Apprazer}{\emph{Code}}}{OpenCV $|$ SKLearn $|$ NextJS}
          \resumeItemListStart
            \resumeItem{Led 4-person team to build a loan preapproval system with OpenCV ROI extraction, achieving 99\% document parsing accuracy while processing only 5\% of each page; won \emph{Best Use of AI in Real Estate} 600 participants.}
            \resumeItem{Built/deployed Random Forest classifier in SKLearn trained on 5M+ records to predict loan decisions, achieving 88\% accuracy; integrated with NextJS for an E2E demo and reproducible evaluation and TensorBoard logging.}
            \resumeItem{Built a production-ready NextJS demo for rapid verification and model introspection using SKLearn pipelines.}
          \resumeItemListEnd
     \resumeProjectHeading
          {\textbf{hhana} $|$ \href{https://github.com/justinsiek/hhana}{\emph{Code}}}{Python $|$ Polars $|$ DuckDB}
          \resumeItemListStart
            \resumeItem{Built ETL pipeline with Polars and DuckDB to process 10 million hand histories, detect population deviations from equilibrium, and emit aggregated nodes used to derive data-driven exploits for downstream MCCFR training.}
            \resumeItem{Implemented MCCFR baseline with softmax utility boosts to capitalize on exploitable population imbalances, performing node aggregation and regret updates to converge strategies; optimized code for experiments now.}
            \resumeItem{Generated data-driven exploits from 10 million hand histories using MCCFR with softmax boosts for analysis.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++} \\
     \textbf{Frameworks}{: Flask} \\
     \textbf{Libraries}{: Pytorch, OpenCV, numpy, matplotlib, SKLearn, Tensorflow} \\
     \textbf{Developer Tools}{: Git, Docker, AWS} 
     }}
 \end{itemize}


%-------------------------------------------
\end{document}
